---
title: "Assignment 1"
author: "Matthew Reynolds"
date: "22 March 2023"
output: html_notebook
---

Introduction:
Following along with "Introduction to Statistical Learning First Edition" from www.statlearning.com
This is Exercise #8 in Chapter 2, findable at Page 55.


A) Use the read.csv() function to read the data into R. Call the loaded data college. Make sure that you have the directory set to the correct location for the data.
```{r}
college <- read.csv("https://www.statlearning.com/s/College.csv")
```

B) Look at the data using the fix() function. You should notice that the first column is just the name of each university. We don’t really want R to treat this as data. However, it may be handy to have these names for later.
```{r}
rownames(college)=college[,1]
head(college)
```
You should see that there is now a row.names column with the name of each university recorded. This means that R has given each row a name corresponding to the appropriate university. R will not try to perform calculations on the row names. However, we still need to eliminate the first column in the data where the names are stored.
```{r}
college=college[,-1]
head(college)
```
Now you should see that the first data column is Private. Note that another column labeled row.names now appears before the Private column. However, this is not a data column but rather the name that R is giving to each row.

C)
  I) Use the summary() function to produce a numerical summary of the variables in the data set.
```{r}
summary(college)
```
  II) Use the pairs() function to produce a scatterplot matrix of the first ten columns or variables of the data. Recall that you can reference the first ten columns of a matrix A using A[,1:10].
```{r}
# Changing Private to a factor variable
college$Private <- as.factor(college$Private)

pairs(college[,1:10])
```
  III) Use the plot() function to produce side-by-side boxplots of Outstate versus Private.
```{r}
plot(college$Private, college$Outstate, xlab = "Private University?", ylab = "Cost of Tuition")
```
  IV) Create a new qualitative variable, called Elite, by binning the Top10perc variable. We are going to divide universities into two groups based on whether or not the proportion of students coming from the top 10% of their high school classes exceeds 50 %.
```{r}
# Provided from textbook
Elite=rep("No",nrow(college))
Elite[college$Top10perc >50]="Yes"
Elite=as.factor(Elite)
college=data.frame(college ,Elite)
```
  Use the summary() function to see how many elite univer- sities there are. Now use the plot() function to produce side-by-side boxplots of Outstate versus Elite.
```{r}
summary(Elite)
plot(college$Elite, college$Outstate, xlab="Elite University?", ylab="Cost of tuition")
```
  V) Use the hist() function to produce some histograms with differing numbers of bins for a few of the quantitative vari- ables. You may find the command par(mfrow=c(2,2)) useful: it will divide the print window into four regions so that four plots can be made simultaneously. Modifying the arguments to this function will divide the screen in other ways.
```{r}
# Fragmenting the display
par(mfrow=c(2,2))

# Creating the histograms
hist(college$Outstate, col = 4, xlab = "# of out of state students", main = "")
hist(college$Apps, col = 3, xlab = "# of applications", main = "")
hist(college$Grad.Rate, col = 2, xlab = "Rate of Graduation", main = "")
hist(college$Accept, col = 5, xlab = "Rate of Acceptance", main = "")
```
  VI) Continue exploring the data, and provide a brief summary of what you discover.
```{r}
# Number of PhD professors correlation to graduation rate
plot(college$PhD, college$Grad.Rate)
```
```{r}
# School with highest amount from top 10 percent of high school class
row.names(college)[which.max(college$Top10perc)] 
```
  

