---
title: "Exercise8"
author: "Matthew Reynolds"
date: "2023-04-03"
output: html_document
---

<b>Introduction:</b>\
Following along with Chapter 7 of "Introduction to Statistical Learning First Edition" from www.statlearning.com.

<b>Exercise #8:</b>\
Fit some of the non-linear models investigated in this chapter to the Auto data set. Is there evidence for non-linear relationships in this data set? Create some informative plots to justify your answer. \
\

<b>Initial data exploration:</b>
```{r, message = FALSE}
library(GGally)
library(ISLR)
pairs(Auto)
```
<center><i>It would appear that the correlation between MPG and seemingly everything is non-linear.</i></center>\

```{r, message = FALSE}
ggplot(Auto, aes(x = displacement, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```
```{r, message = FALSE}
ggplot(Auto, aes(x = horsepower, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

```{r, message = FALSE}
ggplot(Auto, aes(x = weight, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

```{r, message = FALSE}
ggplot(Auto, aes(x = acceleration, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

```{r, message = FALSE}
ggplot(Auto, aes(x = year, y = mpg)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```

<b>Answer:</b>
\
<center><i>I would definetly say there's non linear relationships in this data. All of those graphs are clearly non linear. Especially the mpg x acceleration (second from bottom).</i></center>\
\
\


